Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-11 scnn.tex
end of the day

\subsection{Spherical convolutions} 
The major challenge to define Convolution Neural Network (CNN) onto a
spherical domain is to handle a convolution suitable for this irregular domain. 
We found two particular approaches to address this issue.

The first approach, leveraging the continuous spherical convolution, has been
proposed in~\cite{cohen2017convolutional,cohen2018spherical}. These
contributions propose to use a convolution that is rotational equivariant on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The convolution is performed by a spherical Fourier transform (i.e. a projection
on the spherical harmonics), a  multiplication in the spectral domain and an
inverse spherical Fourier tranform. Hence the main computational cost of a
convolution comes from the two Fourier transforms. Fortunately, the Fourier
transform can be accelerated for special samplings set (theoretically including
HealPix). The main advantage of this approach is that it provides a
mathematically well defined rotational equivariant network. Nevertheless, even
with these Fourier transform acceleration, the convolutions remain expensive in
comparison to a traditional 2-dimensional convolution, limiting the practical use of this
approach. While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the Healpix one. Hence, a practical comparison is
not possible.

>>>>

\subsection{Spherical convolutions} 
The major challenge to define Convolution Neural Network (CNN) onto a
spherical domain is to handle a convolution suitable for this irregular domain. 
They exist three approaches to address this issue.

The first approach, leveraging the continuous spherical convolution, has been
proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of these
contributions it to use a rotational equivariant convolution on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The resulting convolution is performed by a spherical Fourier transform (i.e. a projection
on the spherical harmonics), a  multiplication in the spectral domain and an
inverse spherical Fourier transform. Hence the main computational cost of a
convolution comes from the two Fourier transforms. Fortunately, the Fourier
transform can be accelerated for special samplings set (theoretically including
HealPix, \cite{...}). The main advantage of this approach is that it provides a
mathematically well defined rotational equivariant network. Nevertheless, even
with these Fourier transform acceleration, the convolutions remain expensive in
comparison to a traditional 2-dimensional convolution, limiting the practical use of this
approach. While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the Healpix one. Hence, a practical comparison is
not possible.
